Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-08-20 review_article.Rmd
part arrange tiles by country

plot1 <- png::readPNG('cancer_map_images/choropleths/15.choropleth.png')
plot2 <- png::readPNG('cancer_map_images/choropleths/25.choropleth.png')
plot3 <- png::readPNG('cancer_map_images/choropleths/1.png')
plot4 <- png::readPNG('cancer_map_images/choropleths/29.choropleth.png')
plot5 <- png::readPNG('cancer_map_images/choropleths/30.choropleth.png')
plot6 <- png::readPNG('cancer_map_images/choropleths/6.choropleth.png')
plot7 <- png::readPNG('cancer_map_images/choropleths/8.choropleth2.png')
plot8 <- png::readPNG('cancer_map_images/choropleths/20.choropleth1.png')
plot9 <- png::readPNG('cancer_map_images/choropleths/7.choropleth.png')
plot10 <- png::readPNG('cancer_map_images/choropleths/23.choropleth.png')
plot11 <- png::readPNG('cancer_map_images/choropleths/24.choropleth.png')
plot12 <- png::readPNG('cancer_map_images/choropleths/14.choropleth1.png')
plot13 <- png::readPNG('cancer_map_images/choropleths/26.choropleth.png')
plot14 <- png::readPNG('cancer_map_images/choropleths/27.choropleth.png')
plot15 <- png::readPNG('cancer_map_images/choropleths/21.choropleth2.png')
plot16 <- png::readPNG('cancer_map_images/choropleths/3.choropleth.png')
plot17 <- png::readPNG('cancer_map_images/choropleths/5.choropleth.png')

>>>>

plot1 <- png::readPNG('cancer_map_images/choropleths/21.choropleth2.png')
plot2 <- png::readPNG('cancer_map_images/choropleths/29.choropleth.png')
plot3 <- png::readPNG('cancer_map_images/choropleths/30.choropleth.png')
plot4 <- png::readPNG('cancer_map_images/choropleths/1.png')
plot5 <- png::readPNG('cancer_map_images/choropleths.2/6.choropleth.png')
plot6 <- png::readPNG('cancer_map_images/choropleths/27.choropleth.png')
plot7 <- png::readPNG('cancer_map_images/choropleths/8.choropleth2.png')
plot8 <- png::readPNG('cancer_map_images/choropleths/20.choropleth1.png')
plot9 <- png::readPNG('cancer_map_images/choropleths.2/7.choropleth.png')
plot10 <- png::readPNG('cancer_map_images/choropleths/23.choropleth.png')
plot11 <- png::readPNG('cancer_map_images/choropleths.2/24.choropleth.png')
plot12 <- png::readPNG('cancer_map_images/choropleths/14.choropleth1.png')
plot13 <- png::readPNG('cancer_map_images/choropleths/26.choropleth.png')
plot14 <- png::readPNG('cancer_map_images/choropleths/15.choropleth.png')
plot15 <- png::readPNG('cancer_map_images/choropleths/25.choropleth.png')
plot16 <- png::readPNG('cancer_map_images/choropleths/3.choropleth.png')
plot17 <- png::readPNG('cancer_map_images/choropleths/5.choropleth.png')
